Forecasting the 2024 Election: Tight Margins and Swing State Uncertainty

### 2024-11-13 paper/paper.qmd
appendix formatting - NOT rendered as pdf

The rest of this paper is structured as follows:  @sec-mydatasection presents the data sources and methodology, @sec-mymodel presents the forecasting model, then  @sec-myresults followed by  @sec-mydisc, which discusses the results and their implications.  @sec-mylimits concludes with a discussion of the limitations of the study and suggestions for future research, followed by @sec-appenxA with The Washington Post’s pollster methodology, and @sec-appenxB a budgeted idealized methodology.

@@

### Diagnostics
To validate the Bayesian framework, several diagnostic checks were conducted to assess robustness and ensure that underlying assumptions were satisfied. Key among these were convergence assessments and posterior predictive checks. These checks provided a visual representation of how well the predictions align with the observed data. The graph reveals a close overlap between the observed outcomes \(y\) and the replicated predictions ($y_{\text{rep}}$), demonstrating effective capture of the distribution of voter support for Harris. This strong alignment suggests that the approach not only fits the training data well but also generalizes effectively to new observations. The flexibility of this framework allows for the incorporation of prior information and consideration of variability due to pollster and state effects, enhancing overall robustness (Refer to the @sec-appc, [@tbl-pp] for a visual illustration).

@@

# Appendix A: Methodology Analysis of The Washington Post Polling  {#sec-appenxA}
With an evaluation of sampling methodology, recruitment, handling non-response, and questionnaire design, this appendix offers an analysis of the polling methodology used by The Washington Post in collaboration with ABC News. The objective is to analyze these approaches' strengths and weaknesses and determine how they affect polling accuracy.

@@

# Appendix B: Idealized Survey & Methodology - $100K Budget {#sec-appenxB}

@@

# Appendix C {#sec-appc}
* [@tbl-pp]
```{r}
#| include: false
#| warning: false
#| message: false
### Model Validation/Checking ###
# Set seed and create train/test split
set.seed(123)
train_indices <- sample(seq_len(nrow(clean_president_polls)), size = 0.7 * nrow(clean_president_polls))
training_data <- clean_president_polls[train_indices, ]
training_data <- training_data %>%
  mutate(pct_scaled = scale(pct))
testing_data <- clean_president_polls[-train_indices, ]

>>>>

The rest of this paper is structured as follows:  @sec-mydatasection presents the data sources and methodology, @sec-mymodel presents the forecasting model, then  @sec-myresults followed by  @sec-mydisc, which discusses the results and their implications.  @sec-mylimits concludes with a discussion of the limitations of the study and suggestions for future research, followed by Appendix @sec-meth-analysis and @sec-ideal-surv with The Washington Post’s pollster methodology and a budgeted idealized methodology.

@@

### Diagnostics
To validate the Bayesian framework, several diagnostic checks were conducted to assess robustness and ensure that underlying assumptions were satisfied. Key among these were convergence assessments and posterior predictive checks. These checks provided a visual representation of how well the predictions align with the observed data. The graph reveals a close overlap between the observed outcomes \(y\) and the replicated predictions ($y_{\text{rep}}$), demonstrating effective capture of the distribution of voter support for Harris. This strong alignment suggests that the approach not only fits the training data well but also generalizes effectively to new observations. The flexibility of this framework allows for the incorporation of prior information and consideration of variability due to pollster and state effects, enhancing overall robustness (Refer to the @sec-app-pp, [@tbl-pp] for a visual illustration).

@@

# Appendix {-}

# Methodology Analysis of The Washington Post Polling {#sec-meth-analysis}
With an evaluation of sampling methodology, recruitment, handling non-response, and questionnaire design, this appendix offers an analysis of the polling methodology used by The Washington Post in collaboration with ABC News. The objective is to analyze these approaches' strengths and weaknesses and determine how they affect polling accuracy.

@@

# Idealized Survey & Methodology - $100K Budget {#sec-ideal-surv}

@@

# Posterior Predictive Check {#sec-app-pp}
* [@tbl-pp]
```{r}
#| include: false
#| warning: false
#| message: false
### Model Validation/Checking ###
# Set seed and create train/test split
set.seed(123)
train_indices <- sample(seq_len(nrow(clean_president_polls)), size = 0.7 * nrow(clean_president_polls))
training_data <- clean_president_polls[train_indices, ]
training_data <- training_data %>%
  mutate(pct_scaled = scale(pct))
testing_data <- clean_president_polls[-train_indices, ]
